---
title: "Assignment 2"
author: "Sadé Miller"
date: "2/5/2025"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 

1.  **What is the second argument in the `lm()` function?**

    *`? lm()`*

    *The second argument in the `lm()` function is data, which is defined as an optional data frame, list, or environment containing the variables in the model.*

2.  **What is the second argument in the `plot.gam()` function, found in the `mgcv` library?**

    *`library (mgcv)`*

    *`? plot.gam()`*

    *The second argument in the `plot.gam()`function is residuals. If true, partial residuals are added to plots of 1-D smooths. If false, no residuals are added.*

3.  **What is the length of the vector created from a sequence of 3 to 27 by intervals of 0.13?**

    ```{r}
    seq(3, 27, by = 0.13)

    ```

    *The length of the vector is 185.*

4.  **What code subsets the first row and third column of the second matrix for the array `array(seq(1:20), dim=c(2,5,2))`, and what number occupies that position?**

    *The code that subsets the first row, third column of the second matrix is:*

    ```{r}
    T <- array(seq(1:20), dim=c(2,5,2))
    ```

    ```{r}
    T[1,3,2]
    ```

    *The value that occupies that position is 15.*

5.  **Create a list object from 3 or more built in [datasets](https://vincentarelbundock.github.io/Rdatasets/datasets.html){.uri}.**

`X <- data("NaturalGas", "CigarettesB", "ShipAccidents")`

`TestList <- list(CigarettesB, NaturalGas, ShipAccidents) View(TestList)`

6.  **What is the mean length of major North American Rivers?**

```{r}
mean(rivers)
```
*The mean length of major North American Rivers is about 591 miles.* 

7.  **Write a built-in dataset to a CSV file (show code) and open it in Excel.**

`write.csv(mtcars, file= '/Users/sadem/Desktop/mtcars.csv')`

8.  **Tabulate the type and concentration factors in the CO2 dataset in one table. Is this experiment balanced?**

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
CO2 %>% select(Type,conc)
```
```{r, message=FALSE}
library(nlme)
isBalanced(CO2) 
```
*Yes, this experiment is balanced.*

9.  **Write a single function to subset both spray A and records of counts \> 17 from InsectSprays. How many records are there?**

```{r}
filter(InsectSprays, spray == "A", count > 17)
```

*There are 3 records that result from this function.*


10. **In 2005, what was the 5th city in TX for home sales?**

```{r, message=FALSE}
txhousing %>% filter(year == 2005) %>%
group_by(city,year) %>%
summarise(sum_sales = sum(sales)) %>%
arrange(desc(sum_sales))
```

*The 5th city in Texas for home sales in 2005 was Collin County.*


